---
title: "Programming Background"
author: "Steph Camino"
date: "6/6/2022"
---

```{r}
library(knitr)
knitr::opts_chunk$set(fig.path = "../images/")
```

## Second Blog

R was the first statistics programming language I learned so I believe that's why I'm a little biased. I love how user friendly it is and how there's a package for almost everything. I miss ods output from SAS and how easy it was to use. I also miss that SAS wasn't case sensitive. I don't think that R is a difficult language to learn but I was also had a computer science minor in undergrad so I have been exposed to more languages than some others. I first learned R my freshman year of undergrad at the University of Wyoming. It was a statistical methods course with Dr. Scott Crawford. He set up the classroom where we would walk through statistical analyses in class and he would show us how to code step by step. We did this instead of the lecture format. The way he set it up made it very easy to learn R and I'm very thankful to Scott and that course. 

## Example R Markdown Output

```{r}
plot(iris)
```

rmarkdown::render("_Rmd/2022-06-06-Second-Blog-Post.Rmd",
                  output_format = "github_document",
                  output_dir = "_posts", 
                  output_options = list(html_preview = FALSE))

